\section*{FEEDBACKS}
\begin{aspect}{SURVEY QUESTIONS}
	Answering these questions is optional, but it will help us improve the course in future quarters.
	Feel free to tell us anything you wantthese questions are just to spur your thoughts.
	You may also choose to respond anonymously in the course evaluations at the end of the quarter.

	\begin{qc}
		\textbullet
		In your opinion, was this assignment, or any one of the three problems in it, too easy or too hard?
		Did it take too long or too little time?
	\end{qc}
	The programming language C is too weak in the sense of expressiveness and abstraction capability.
	Building and manage such a large code base in C is quite hard. \\
	What make things worst is that the ubquitous design principles and development methodologies in modern software are hard to apply in pintos.\\
	It is just feels like choosing to fight with sticks picked from the river side when you have a gun and powder in your pocket.

	\begin{qc}
		\textbullet
		Did you find that working on a particular part of the assignment gave you greater insight into some aspect of OS design?
	\end{qc}

	\begin{qc}
		\textbullet
		Is there some particular fact or hint we should give students in future quarters to help them solve the problems?
		Conversely, did you find any of our guidance to be misleading?
	\end{qc}

	\begin{qc}
		\textbullet
		Do you have any suggestions for the TAs to more effectively assist students,
		either for future quarters or the remaining projects?
	\end{qc}
	Provide this helpful guide line to them: make things work, then make things work correctly and finally prettify the code and improve the performance.

	\begin{qc}
		\textbullet
		Any other comments?
	\end{qc}
	xv6 and/or ucore seems appealing, would you consider trying them in future CS130?
\end{aspect}



